State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-08-22 draft.tex
Corrected bounds on rho below (3.17) and reinstated the formula for c1

We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set $\mathcal X^\infty$ implies that there exists a finite integer $M$ such that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
The analysis uses $P$-balls $\mathscr B_P(r)$ 
%that contain $\mathcal X_k$ and are contained within $\mathcal R_k$. We define 
where $P$ is a positive definite matrix satisfying 
\begin{equation}\label{eq:Pcondition}
\varrho^2 P \succ \Psi^T P \Psi
\end{equation} 
for some scalar $\varrho\in (0,1)$, so that $\Psi\mathscr B_P(r) \subseteq \varrho\mathscr B_P(r)$ and $\Psi^{-1}\mathscr B_P(r) \supseteq \varrho^{-1}\mathscr B_P(r)$ for all $r>0$. 
Note that $P\succ 0$ and $\varrho$ exist satisfying (\ref{eq:Pcondition}) whenever
%$\Psi$ is assumed to be an asymptotically stable matrix.
$\varrho \leq \rho(\Psi) < 1$
where $\rho(\Psi)$ is the spectral radius of $\Psi$ (see e.g.~\cite{Boyd:94}).

@@

\begin{rem}
The condition that $c_1 > (1-\varrho)^{-1}c_3$ in Theorem~\ref{thm:Mbnd} implies a restriction on the size of the disturbance set $\V(x)$ for $x\in\X$ that might not be met even if $\X^\infty$ is non-empty. To minimize the implied degree of conservativeness therefore the constants $c_1$, $c_2$, $c_3$ appearing in~(\ref{eq:iteration:cbound}) can be computed as follows:
\textcolor{blue}{\[
c_1 = \max_x x^T P x \ \ \text{subject to} \ \  \Xi x\leq {\bf{1}},
\]}
% \[
% c_1 = \min_j\bigl\{\min_x x^T P x \ \ \text{subject to} \ \  \Xi x\leq {\bf{1}},\ \xi_j x = 1\bigr\}
% \]
which requires the solution of a nonconvex quadratic program (QP); 
% which requires the solution of $\abs{\mathcal I_{\mathcal X}}$ quadratic programs (QPs); 
\[
c_2 = \max_{j} x_j^TPx_j,
\]
where 
%$x_j$ for $j\in\mathbb{N}_p$ are the vertices of $\mathcal{P}_n$;
$\mathcal{P}_n  =\conv_j\{x_j\}$; 
and for $c_3$ we can use a projection and the known combinatorial structure of~$\mathcal V(x)$ in the sense of~\eqref{eq:def:v:kappa}.
%
\textcolor{red}{First project the set 
%
$$
  \mathcal T = \bigl\{(\tau,x):\Xi x\leq {\bf{1}},\ b_{i,k}+c_{i,k}x\leq \tau_i \ \forall i\in\mathbb N_m,\ \forall k\bigr\}
$$
onto $\mathbb R^m$, 
thereby all vertices of the projection are such that there exists $\tilde x\in\mathcal X$ such that $\mathcal V(\tilde x)=\conv_\kappa\{v : a_i v = \tau_i, \ i\in\mathcal A_\kappa\}$.
%
Therefore maximising over all vertices of the projection leads to the desired radius 
\[
c_3 = \max_{\tau\in\text{vert}(\pi_m(\mathcal T))}\max_\kappa v_\kappa^TPv_\kappa, \ v_\kappa = \{v : a_i v = \tau_i, \  i\in\mathcal A_\kappa\} .
\]}
%In the interests of minimizing $M$, it makes sense to set $\varrho$ equal to $\rho(\Psi)$, in which case $P = \Psi\Psi^T$.
\end{rem}

>>>>

We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set $\mathcal X^\infty$ implies that there exists a finite integer $M$ such that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
The analysis uses $P$-balls $\mathscr B_P(r)$ 
%that contain $\mathcal X_k$ and are contained within $\mathcal R_k$. We define 
where $P$ is a positive definite matrix satisfying 
\begin{equation}\label{eq:Pcondition}
\varrho^2 P \succ \Psi^T P \Psi
\end{equation} 
for some scalar $\varrho\in (0,1)$, so that $\Psi\mathscr B_P(r) \subseteq \varrho\mathscr B_P(r)$ and $\Psi^{-1}\mathscr B_P(r) \supseteq \varrho^{-1}\mathscr B_P(r)$ for all $r>0$. 
Note that $P\succ 0$ and $\varrho$ exist satisfying (\ref{eq:Pcondition}) whenever
%$\Psi$ is assumed to be an asymptotically stable matrix.
$\rho(\Psi) \leq \varrho < 1$
where $\rho(\Psi)$ is the spectral radius of $\Psi$ (see e.g.~\cite{Boyd:94}).

@@

\begin{rem}
The condition that $c_1 > (1-\varrho)^{-1}c_3$ in Theorem~\ref{thm:Mbnd} implies a restriction on the size of the disturbance set $\V(x)$ for $x\in\X$ that might not be met even if $\X^\infty$ is non-empty. To minimize the implied degree of conservativeness therefore the constants $c_1$, $c_2$, $c_3$ appearing in~(\ref{eq:iteration:cbound}) can be computed as follows:
\[
c_1 = \min_j\{\min_x x^TPx \ \ \text{subject to} \ \  \Xi x\leq {\bf{1}}, \ \xi_j x = 1\}
\]
which requires the solution of $\abs{\mathcal I_{\mathcal X}}$ quadratic programs (QPs);
\[
c_2 = \max_{j} x_j^TPx_j,
\]
where 
%$x_j$ for $j\in\mathbb{N}_p$ are the vertices of $\mathcal{P}_n$;
$\mathcal{P}_n  =\conv_j\{x_j\}$; 
and for $c_3$ we can use a projection and the known combinatorial structure of~$\mathcal V(x)$ in the sense of~\eqref{eq:def:v:kappa}.
%
\textcolor{red}{First project the set 
%
$$
  \mathcal T = \bigl\{(\tau,x):\Xi x\leq {\bf{1}},\ b_{i,k}+c_{i,k}x\leq \tau_i \ \forall i\in\mathbb N_m,\ \forall k\bigr\}
$$
onto $\mathbb R^m$, 
thereby all vertices of the projection are such that there exists $\tilde x\in\mathcal X$ such that $\mathcal V(\tilde x)=\conv_\kappa\{v : a_i v = \tau_i, \ i\in\mathcal A_\kappa\}$.
%
Therefore maximising over all vertices of the projection leads to the desired radius 
\[
c_3 = \max_{\tau\in\text{vert}(\pi_m(\mathcal T))}\max_\kappa v_\kappa^TPv_\kappa, \ v_\kappa = \{v : a_i v = \tau_i, \  i\in\mathcal A_\kappa\} .
\]}
%In the interests of minimizing $M$, it makes sense to set $\varrho$ equal to $\rho(\Psi)$, in which case $P = \Psi\Psi^T$.
\end{rem}
